mlr_assg4

### 2022-09-20 hw4-1/abhinav/mlr.Rmd
WIP-abhinav

```{r}
options(scipen=999)
crime_data$So<-as.factor(crime_data$So)
# Linear Regression model with all features
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data)
summary(lmodel_1)
# plotting the residuals to check for assumptions in the plain vanilla model with all features
par(mfrow = c(2, 2))
plot(lmodel_1)
```

```{r}
# removing all the potential outliers/influential points based on the diagnostic plots of linear regression model
crime_data_wo<-crime_data[-c(11,46,29),]
dim(crime_data_wo)
# Linear Regression model with all features on the reduced dataset
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_1)
```

```{r}
new_datapoint<-data.frame(M=c(14.0),So=c(as.factor(0)),Ed=c(10.0),Po1=c(12.0),Po2=c(15.5),LF=c(0.640),M.F=c(94.0),Pop=c(150),NW=c(1.1),U1=c(0.120),U2=c(3.6),Wealth=c(3200),Ineq=c(20.1),Prob=c(0.04),Time=c(39.0))
crime_rate_pred<-predict(lmodel_1,newdata = new_datapoint)
crime_rate_pred
```

@@

```{r}
crime_data_wo<-crime_data[-c(11,19,29),]
dim(crime_data_wo)
# Linear Regression model with all features
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_1)
# Linear Regression Model with Limited features (removing highly correlated features)
lmodel_4<-lm(Crime~M+So+Ed+Po1+LF+M.F+Pop+NW+U1+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_4)

@@

```{r}
crime_data_wo<-crime_data[-c(11,19,29,46),]
dim(crime_data_wo)
# Linear Regression model with all features
lmodel_5<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_5)
# Linear Regression Model with Limited features (removing highly correlated features)
lmodel_6<-lm(Crime~M+So+Ed+Po1+LF+M.F+Pop+NW+U1+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_6)

>>>>

```{r}
options(scipen=999)
crime_data$So<-as.factor(crime_data$So)
# Linear Regression model with all features
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data)
summary(lmodel_1)
# plotting the residuals to check for assumptions in the plain vanilla model with all features
par(mfrow = c(2, 2))
plot(lmodel_1)

new_datapoint<-data.frame(M=c(14.0),So=c(as.factor(0)),Ed=c(10.0),Po1=c(12.0),Po2=c(15.5),LF=c(0.640),M.F=c(94.0),Pop=c(150),NW=c(1.1),U1=c(0.120),U2=c(3.6),Wealth=c(3200),Ineq=c(20.1),Prob=c(0.04),Time=c(39.0))
crime_rate_pred<-predict(lmodel_1,newdata = new_datapoint)
crime_rate_pred
```

```{r}
options(scipen=999)
crime_data$So<-as.factor(crime_data$So)
# Linear Regression model with all features
lmodel_2<-lm(log(Crime)~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data)
summary(lmodel_2)
# plotting the residuals to check for assumptions in the plain vanilla model with all features
par(mfrow = c(2, 2))
plot(lmodel_2)

new_datapoint<-data.frame(M=c(14.0),So=c(as.factor(0)),Ed=c(10.0),Po1=c(12.0),Po2=c(15.5),LF=c(0.640),M.F=c(94.0),Pop=c(150),NW=c(1.1),U1=c(0.120),U2=c(3.6),Wealth=c(3200),Ineq=c(20.1),Prob=c(0.04),Time=c(39.0))
crime_rate_pred<-predict(lmodel_2,newdata = new_datapoint)
crime_rate_pred<- exp(crime_rate_pred)
crime_rate_pred
```

```{r}
# removing the potential outliers/influential points based on the diagnostic plots of linear regression model
crime_data_wo<-crime_data[-c(11, 19, 46),]
dim(crime_data_wo)
# Linear Regression model with all features on the reduced dataset
lmodel_2<-lm(log(Crime)~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_2)
```

```{r}
new_datapoint<-data.frame(M=c(14.0),So=c(as.factor(0)),Ed=c(10.0),Po1=c(12.0),Po2=c(15.5),LF=c(0.640),M.F=c(94.0),Pop=c(150),NW=c(1.1),U1=c(0.120),U2=c(3.6),Wealth=c(3200),Ineq=c(20.1),Prob=c(0.04),Time=c(39.0))
crime_rate_pred<-predict(lmodel_4,newdata = new_datapoint)
crime_rate_pred
```
```{r}
crime_data[c(4,26),]
```

@@

```{r}
crime_data_wo<-crime_data[-c(11,19,29),]
dim(crime_data_wo)
# Linear Regression model with all features
lmodel_1<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_1)
# Linear Regression Model with Limited features (removing highly correlated features)
lmodel_4<-lm(Crime~M+So+Ed+Po1+LF+M.F+Pop+NW+U1+Ineq+Prob+Time,data=crime_data)
summary(lmodel_4)

@@

```{r}
crime_data_wo<-crime_data[-c(11,19,29,46),]
dim(crime_data_wo)
# Linear Regression model with all features
lmodel_5<-lm(Crime~M+So+Ed+Po1+Po2+LF+M.F+Pop+NW+U1+U2+Wealth+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_5)
# Linear Regression Model with Limited features (removing highly correlated features)
lmodel_6<-lm(Crime~M+So+Ed+Po1+LF+M.F+Pop+NW+U1+Ineq+Prob+Time,data=crime_data_wo)
summary(lmodel_6)
```
